Assessing Ranking Fidelity of Competition Structures via Weighted Mutual Information

### 2025-10-17 CMSAC_presentation/josie_slides.qmd
josie slides but having issues

---
title: "Assessing Ranking Fidelity of Competition Structures via Weighted Mutual Information"
author: "Zach Culp, Josie Peterburs, Dr. Gregory J. Matthews, Dr. Ryan P.A. McShane"
format: revealjs
editor: visual
date: "`r Sys.Date()`"
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tinytex)
library(tidyverse)
library(combinat)
load("curves_data.RData")
#load("tournament_comparison_plot.png")
#load("tournament_comparison_plot_close.png")
```

@@

```{r}
knitr::include_graphics("4 bracket good.png")
```

@@

:::: {.columns}

::: {.column width="50%"}
Good 
:::

::: {.column width="50%"}
Bad
:::

::::

@@

- **Efficacy**^[Lasek and Gagolewsk (2018), Sziklai, Biró, and Csató (2022)]: Final rankings should match the true rankings of the strength of the competitors

- **Effectivity**^[Glenn (1960)]: Interested in correctly ranking the best competitor as first

@@

- Decide how many rankings are important
  - Olympic competition ranks the top 3 competitors
  - Premier League: top 4 (Champions League) and bottom 3 (Relegation)

- **Salient ranks**: the ranks that matter
  - Efficacy: 1 through $n$ matter
  - Effectivity: 1 is only salient rank

>>>>

---
title: "Assessing Ranking Fidelity of Competition Structures via Weighted Mutual Information"
author: "Zach Culp, Josie Peterburs, Dr. Gregory J. Matthews, Dr. Ryan P.A. McShane"
format: revealjs
editor: visual
date: "`r Sys.Date()`"
bibliography: ../references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tinytex)
library(tidyverse)
library(combinat)
# load("curves_data.RData")
#load("tournament_comparison_plot.png")
#load("tournament_comparison_plot_close.png")
```

@@

::::: columns
::: {.column width="50%"}
```{r}
knitr::include_graphics("4 bracket good.png")
```
:::

::::: columns
::: {.column width="50%"}
```{r}
knitr::include_graphics("Mens-Basketball-Olympics-Getty-H-2024.jpeg")
knitr::include_graphics("five_rec_league_men_playing_basketball.png")
knitr::include_graphics("jv_girls_basketball.png")
knitr::include_graphics("five_babies_playing_basketball.png")

```
:::
:::::

@@

::::: columns
::: {.column width="50%"}
Good
:::

::: {.column width="50%"}
Bad
:::
:::::

@@

-   **Efficacy**[^1]: Final rankings should match the true rankings of the strength of the competitors

-   **Effectivity**[^2]: Interested in correctly ranking the best competitor as first

[^1]: Lasek and Gagolewsk (2018), Sziklai, Biró, and Csató (2022)

[^2]: Glenn (1960)

@@

-   Decide how many rankings are important
    -   Olympic competition ranks the top 3 competitors
    -   Premier League: top 4 (Champions League) and bottom 3 (Relegation)
-   **Salient ranks**: the ranks that matter
    -   Efficacy: 1 through $n$ matter
    -   Effectivity: 1 is only salient rank
